\documentclass[12pt,letterpaper]{scrreprt}

%----------------------------------------------------------------------
%				Required Packages
%----------------------------------------------------------------------
\usepackage{usecases}
\usepackage{enumitem}
%\usepackage{paralist}
%\usepackage{tabto}
\usepackage[top=2cm,bottom=3.5cm]{geometry}

%----------------------------------------------------------------------
%				Title Page
%----------------------------------------------------------------------
\title{CS383: Software Engineering}
\subtitle{HW2: Use Cases\\Fall 2013}
\author{CS383 Python Team} % Include everyone's name?
\date{}

%----------------------------------------------------------------------
%				Additional Settings
%----------------------------------------------------------------------
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}




%----------------------------------------------------------------------
%				Use Case Document Start
%----------------------------------------------------------------------
\begin{document}

% Initializations
%\NumTabs{2} % This is for creating a two column use case scenario
\maketitle
%\tableofcontents % Eventually uncomment this

\chapter{Use cases}
        \section{Pre-Game}
                \subsection{Use Case - Pre-game I: Setting up the Player(s)}
                \begin{usecase}
                  \addtitle{Pre-game I}{Setting up the Player(s)}
                  \addfield{Summary}{The players connect with each other.}
                  \additemizedfield{Actors}{
                    \item Human player(s)
                  }
                  \additemizedfield{Preconditions}{
                    \item Game client(s) and server(s) have been started
                  }
                  \additemizedfield{Primary Scenario: Multi-player}{
                    \item Players adjust settings and ensure general connectivity
                    \item Players find each other either via server matching or other communication
                    \item Players connect to each other for the game-start
                    \item Players choose a side, one of:
                      \begin{enumerate}
                        \item Rebel Player
                        \item Imperial Player
                      \end{enumerate}
                  }
                  \additemizedfield{Alternative Scenario: Single-player}{
                    \item Player adjusts settings
                    \item Player chooses side, one of:
                      \begin{enumerate}
                        \item Rebel Player
                        \item Imperial Player
                      \end{enumerate}
                    \item Player chooses AI difficulty level
                  }
                 \end{usecase}
                \subsection{Use Case - Pre-game II: Choosing the Game}
                \begin{usecase}
                  \addtitle{Pre-game II}{Choosing the Game}
                  \addfield{Summary}{The players choose a type of game
                    before scenario selection.}
                  \additemizedfield{Actors}{
                        \item Rebel Player
                        \item Imperial Player
                  }
                  \additemizedfield{Preconditions}{
                        \item Player match-up has been completed
                        \item Computer and Network players have been set-up
                  }
                  \additemizedfield{Primary Scenario: Multi-player}{
                        \item The players vote to agreement on one of the following games:
                              \begin{enumerate}
                                    \item Star-system Game
                                    \item Province Game
                                    \item Galactic Game
                              \end{enumerate}
                  }
                  \additemizedfield{Alternative Scenario: Single-player}{
                        \item If single-player, the human player chooses one of:
                              \begin{enumerate}
                                    \item Star-system Game
                                    \item Province Game
                                    \item Galactic Game
                              \end{enumerate}
                  }
                \end{usecase}
                \subsection{Use Case - Pre-game III: Choosing the Scenario}
                \begin{usecase}
                  \addtitle{Pre-game III}{Choosing the Scenario}
                  \addfield{Summary}{The players choose from among the
                    available scenarios for their chosen game.}
                  \additemizedfield{Actors}{
                    \item Imperial Player
                    \item Rebel Player
                  }
                  \additemizedfield{Preconditions}{
                    \item Game type has been chosen
                  }
                  \additemizedfield{Primary Scenario: Star-System Game}{
                    \item The system displays the Star-System game scenarios and their information
                          \begin{enumerate}
                                \item Flight to Egrix
                                \item The Varu Powderkeg
                          \end{enumerate}
                    \item The players vote to agreement on which scenario to play
                  }
                  \additemizedfield{Alternative Scenario: Province Game}{
                    \item The system displays the Province game scenarios and their information
                        \begin{enumerate}
                              \item The Empire's Backdoor
                              \item Orlog Besieged
                        \end{enumerate}
                    \item The players vote to agreement on which scenario to play
                  }
                  \additemizedfield{Alternative Scenario: Galactic Game}{
                    \item There is only one scenario for the Galactic Game, and that is the Campaign
                    \item The players
                  }
                \end{usecase}
        \section{Game opening}
                \subsection{Use Case - Game opening: Set-up Chosen Scenario}
                % I think this is where Game Opening comes into play, the scenario needs to be set-up which means
                % that the player(s) need to place all their characters/units
	\section{Missions}
		\subsection{Use Case - Missions I: Mission Phase}
		% Missions Overview Use Case
		\begin{usecase}
		\addtitle{Missions I}{Mission Phase}
		\addfield{Summary}{The phasing player goes on missions to try and gain resources of some sort to help him/her win the game.  Missions are chosen and completed on a per-Environ basis.}
		\additemizedfield{Actors}{
			\item Phasing Player
		}
		\additemizedfield{Preconditions}{
			\item Search Phase has been completed.
			\item Phasing player has characters that are eligible to complete missions.
			}
		\addscenario{Primary Scenario}{
			\item Phasing Player chooses Environ.
			\item System determines and displays eligible characters.
			\item Phasing Player groups characters into Mission Groups.
				\begin{enumerate}
				\item If Phasing Player controls Rebel Camp in selected Environ, it is also an eligible Mission Group.
				\end{enumerate}
			\item System displays eligible Missions.
			\item Phasing Player chooses Missions.
			\item Phasing Player assigns Missions to Mission Groups.
			\item Phasing Player attempts to complete Missions.
			\item Phasing Player chooses next Environ to complete Missions in and repeats until no eligible Characters remain.
		}
		\addscenario{Alternative Scenario: No Missions}{
			\item Phasing Player may choose not to complete any Missions.  In this case, the Mission Phase is complete.
		}
		\addscenario{Alternative Scenario: Cancel Missions}{
			\item Phasing Player may choose to Abort a mission at any time.  Any incomplete Missions are then considered Aborted.
		}
		\additemizedfield{Related Use Cases}{
			\item Missions II: Completing Missions in One Environ
		}
		\end{usecase}
		
		\subsection{Use Case - Missions II: Completing Missions in One Environ}
		\begin{usecase}
		\addtitle{Missions II}{Completing Missions in One Environ}
		\addfield{Summary}{The Phasing Player attempts to complete Missions by completing the Events chosen by the System.
		}
		\additemizedfield{Actors}{
			\item Phasing Player (regularly)
			\item Non-Phasing Player (occasionally)
		}
		\additemizedfield{Preconditions}{
			\item Mission Groups have been chosen, and Missions have been Assigned.
		}
		\addscenario{Primary Scenario}{
			\item System determines number of ``Mission Attempts'' and determines Action Events for each Attempt.
			\item Phasing Player completes Action Event.
				\begin{enumerate}
					\item Non-Phasing Player may be involved with an Action Event.
				\end{enumerate}
			\item Missions are completed based on results of Action Event.
			\item Phasing Player continutes until:
				\begin{enumerate}
				\item All Missions are completed (successfully or unsuccessfully) or Aborted.
				\item No Mission Attempts remain.
				\end{enumerate}
			\item System calculates results of Bonus Mission Attempts for incomplete missions.
		}
		\end{usecase}

		
		
\end{document}